### 2013-07-23 Tex/chapters/model.tex
Fehler bei Definition der Hamilton Funktion
Torus hinzugefügt

        H = \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i \tilde{H}_i s_i

@@

    In subsequent graphics, the graphs will be unrolled and shown as a
    planar projection. Connections which cross a periodic boundary are
    indicated by edges which connect to an dashed node.

@@

        %~ \includegraphics[width=0.3\textwidth]{images/torusRNG.pdf}

@@

            A graph on a torus to visualise periodic boundary conditions.

>>>>

        H = - \sum_{\avg{i,j}}J_{ij}s_{i}s_{j} - \sum_i \tilde{H}_i s_i

@@

    In subsequent graphics, the graphs will be unwrapped to rectangular
    shapes. Connections which cross a periodic boundary are indicated
    by edges which connect to an dashed node.

@@

        \includegraphics[width=0.45\textwidth]{images/torus}

@@

            A graph on a torus to visualize periodic boundary conditions.
            Note that the lattice on this torus is not a square but has
            a height to width ratio of 1:4. At 1:1 the torus would cut
            itself. Also the shades are of course only a guide to the eye.
